Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-28 research_proposal/research_proposal.qmd
refine

When forecasting sales for items in a cafe, such as matcha latte and mocha, the forecasts for each of these drinks (110 matcha lattes and 90 mochas) are often not consistent with the overall sales forecast for the cafe (180 drinks). This is an example of hierarchical time series, where the individual forecasts do not satisfy the linear constraints of different levels of aggregation. Forecast reconciliation comes in to solve this problem, where the individual forecasts are adjusted to satisfy the linear constraints. Among the various reconciliation methods, the **MinT** (Minimum Trace) is considered the optimal approach. However, this method requires an estimate of the covariance matrix of the base forecast errors. In this project, we aim to assess the forecasting performance of MinT when different covariance estimators are used, namely NOVELIST (NOVEL Integration of the Sample and Thresholded Covariance), POET (Principal Orthogonal complEment Thresholding), and others.

@@

![**Fig. 1.** Diagram of 2-level hierarchical tree structure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/hierarchical_structure.png)

>>>>

When forecasting sales for items in a cafe, such as matcha latte and mocha, the forecasts for each of these drinks (110 matcha lattes and 90 mochas) are often not consistent with the overall sales forecast for the cafe (180 drinks). This is a problem of forecasting hierarchical time series, where the individual forecasts do not satisfy the linear constraints of different levels of aggregation. Forecast reconciliation comes in to solve this problem, where the individual forecasts are adjusted to satisfy the given constraints. Among the various reconciliation methods, the **MinT** (Minimum Trace) is considered the optimal approach. However, this method requires an estimate of the covariance matrix of the base forecast errors. The current practice is to use the shrinkage estimator (often shrinking toward a diagonal matrix), but it lacks flexibility and might neglect the prominent structure presented. In this project, we aim to assess the forecasting performance of MinT when different covariance estimators are used, namely NOVELIST (NOVEL Integration of the Sample and Thresholded Covariance), POET (Principal Orthogonal complEment Thresholding), and others.

@@

![Diagram of 2-level hierarchical tree structure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/hierarchical_structure.png){width="40%"}
